---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
dir <- tempfile()
dir.create(dir)
knitr::opts_knit$set(root.dir = dir)
library(archive)
```

# archive
[![Travis-CI Build Status](https://travis-ci.org/jimhester/archive.svg?branch=master)](https://travis-ci.org/jimhester/archive)

R bindings to libarchive <http://www.libarchive.org>, providing support for
many file archives, including tar, ZIP, 7-zip, RAR, CAB including those
compressed by gzip, bzip2, compress, lzma, xz, and others.

## Installation

You can install archive from github with:


``` r
# install.packages("devtools")
devtools::install_github("jimhester/archive")
```

## Example

### Single file archives

```{r}
# Write a single dataset to zip
readr::write_csv(mtcars, archive_write("mtcars.zip", "mtcars.csv"))

# Read the data back, by default the first file is read from the archive.
readr::read_csv(archive_read("mtcars.zip"))

# Also supports archiving and compression together
# Write a single dataset to zip
readr::write_csv(mtcars, archive_write("mtcars.tar.gz", "mtcars.csv"))

# Read the data back
readr::read_csv(archive_read("mtcars.tar.gz"))

# Archive file sizes
file.size(c("mtcars.zip", "mtcars.tar.gz"))
```

### Multi file archives

```{r}
# Write a few files to the temp directory
readr::write_csv(iris, "iris.csv")
readr::write_csv(mtcars, "mtcars.csv")
readr::write_csv(airquality, "airquality.csv")

# Add them to a new archive
archive_write_files("data.tar.xz", c("iris.csv", "mtcars.csv", "airquality.csv"))

# View archive contents
a <- archive("data.tar.xz")

# Read a specific file from the archive
readr::read_csv(archive_read(a, "mtcars.csv"))
```

### Regular files (with compression)
`file_write()` returns a connection to filtered by one or more compressions or encodings.

```{r}
# Write bzip2, base 64 encoded data
readr::write_csv(mtcars, file_write("mtcars.bz2", c("b64encode", "bzip2")))
```
