---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
dir <- tempfile()
dir.create(dir)
knitr::opts_knit$set(root.dir = dir)
options(tibble.print_min = 4L)
library(archive)
```
# archive

<!-- badges: start -->
[![R-CMD-check](https://github.com/jimhester/archive/workflows/R-CMD-check/badge.svg)](https://github.com/jimhester/archive/actions)
[![Coverage Status](https://img.shields.io/codecov/c/github/jimhester/archive/master.svg)](https://codecov.io/github/jimhester/archive?branch=master)
[![Codecov test coverage](https://codecov.io/gh/jimhester/archive/branch/master/graph/badge.svg)](https://codecov.io/gh/jimhester/archive?branch=master)
<!-- badges: end -->

R bindings to libarchive <http://www.libarchive.org>, providing support for
many file archives, including tar, ZIP, 7-zip, RAR, CAB and
compressed by gzip, bzip2, compress, lzma, xz, and others.

## Installation

You can install archive from github with:


``` r
# install.packages("devtools")
devtools::install_github("jimhester/archive")
```

## Example

### Single file archives

```{r}
library(readr) # read_csv(), write_csv(), cols()

# Write a single dataset to zip
write_csv(mtcars, archive_write("mtcars.zip", "mtcars.csv"))

# Read the data back, by default the first file is read from the archive.
read_csv(archive_read("mtcars.zip"), col_types = cols())

# Also supports archiving and compression together
# Write a single dataset to zip
write_csv(mtcars, archive_write("mtcars.tar.gz", "mtcars.csv"))

# Read the data back
read_csv(archive_read("mtcars.tar.gz"), col_types = cols())

# Archive file sizes
file.size(c("mtcars.zip", "mtcars.tar.gz"))
```

### Multi file archives

```{r}
# Write a few files to the temp directory
write_csv(iris, "iris.csv")
write_csv(mtcars, "mtcars.csv")
write_csv(airquality, "airquality.csv")

# Add them to a new archive
archive_write_files("data.tar.xz", c("iris.csv", "mtcars.csv", "airquality.csv"))

# View archive contents
a <- archive("data.tar.xz")
a

# Read a specific file from the archive
read_csv(archive_read(a, "mtcars.csv"), col_types = cols())
```

### Regular files (with compression)
`file_write()` returns a connection to filtered by one or more compressions or
encodings. `file_read()` reads a compressed file, automatically detecting the
compression used.

```{r}
# Write bzip2, base 64 encoded data
write_csv(mtcars, file_write("mtcars.bz2", c("uuencode", "bzip2")))

# Read it back
read_csv(file_read("mtcars.bz2"), col_types = cols())
```
